|

### 2021-04-07 04-Chp-Systematic-Review.Rmd
End of day: 0

### Risk of bias assessment

@@

At present, no risk of bias assessment tool for Mendelian randomization studies is available. Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE]

Data will be visualized using a paired forest and risk of bias plot, created using the `robvis` tool. This tool was developed as part of this thesis to aid in creating standard risk-of-bias figures, and is summarized in Appendix \@ref(appendix-robvis).[@mcguinness2019]

The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020]

A copy of the is available in Appendix \@ref(appendix-mr-rob). Advance results from this review were obtained from contact with the authors.

@@

## Triangualtion across evidence sources

@@

While these preprint have subsequently

@@

Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [ALSO CITE WILKINSON AND MCGUINNESS HERE].

@@

I believe there are three aspects where this review is distinct from those reviews already available in the published literature (as identified by [CITE]):

>>>>

### Risk of bias assessment {#risk-of-bias}

@@

I opted to use the ROBINS-E tool, despite it still being in development,[@morganr2020] in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] There are two primary reasons for this: firstly, current thinking in assessing internal validity has moved away from scales.

Secondly, using a domain based to assess the risk of bias in studies of exposure allowed for better comparison and consistency across the tool used for different study designs, as they are all domain based.

At present, no risk of bias assessment tool for Mendelian randomization studies is available. Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE] The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020] A copy of the is available in Appendix \@ref(appendix-mr-rob). Advance results from this review were obtained from contact with the authors.

Results from the risk-of-bias assessment will be visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool. This tool was developed as part of this thesis to aid in creating standard risk-of-bias figures, and is summarized in Appendix \@ref(appendix-robvis).[@mcguinness2019]

@@

### Triangualtion across evidence sources

@@

On further investigation, the argument that .

It is not so much that they provide a source of unpublished grey-literature, more so that they provide a "future" look at .

However, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a requirement.

While concerns have been raised that

Previous meta-studies have found high concordance between the main interpretations and other study design details in preprint-journal article pairs,[@shi2021] though quality of reporting was slightly better in formally published articles.[@carneiro2020]

A common criticism of preprinted articles is that they have not formally been peer-reviewed. __[CITATION NEEDED]__ However, I believe this criticism is less warranted in the context of inclusion of preprints in a systematic review, given a formal assessment of risk of bias, which provides a structured approach to assessing the internal validity of a study.

> Anyone who can't assess a study to the level of peer review shouldn't do a systematic review

References included in the review were also searched for on PubPeer, a platform which enables post-publication peer review of published journal articles.[@hunter2012]

The added value of peer-review to papers that is questionable and difficult to quantify for a number of reasons, including the fact that most peer reviews are closed

While [__some__] preprint have subsequently been published, this does not cause any major issues.

@@

Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] __[ALSO CITE WILKINSON AND MCGUINNESS HERE]__.

@@

I believe there are three aspects where this review is distinct from those reviews already available in the published literature (as identified by __[CITATION NEEDED]__):

### 2021-04-07 06-Chp-IPD-Analysis.Rmd
Updates
End of day: 0

## Data sources

@@

@@

Letters sent to

This is likely due to my junior position as a ECR

Range of reasons why

>>>>

## Methods

### Data sources

Several cohort studies were approach

<!-- Need exact number approach -->

@@

## Risk of bias assessment

Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).

<!--- Inlcude CPRD analysis here, but dou --->

## Data cleaning

@@

Letters sent to all cohorts identified through the

This is likely due to my junior position as a early a

Range of reasons why data is not made available.

Unfortunately,

As part of this,

As part of this, an analysis of

Describe your experience of trying to access the DPUK - while a great resources, furstrating at times.

### 2021-04-07 front-and-back-matter/99-appendices.Rmd
End of day: 0

@@

@@

@@

@@

-\> NEED TO ADD DATA HERE!

>>>>

### Publications beyond the scope of this thesis {#appendix-publications}

__Peer reviewed__

  * McGuinness & Sheppard. Comparison of pairwise

  * PRISMA main paper

  * PRISMA E&E

  * PRISMA 2020 software

  * COVID Suicide Living Review

  * Data extraction tools systematic review

<!-- Essentially, look at the Trello -->
__Under review/Preprints__

  * MSc Paper on systematic reviews of this thesis topic

  *

### Involvement of patients and the public {#appendix-ppi}

Patients were involved at several stages of this research. when designing the PhD programme of work, a Patient and Public Advisory Group (PPAG) provided feedback on the relevance of the question.

Additionally,

Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement panel. They provide a plain language summary

@@

Note

@@

## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}

### Code lists

@@

All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]

@@

__NEED TO ADD DATA HERE!__

### 2021-04-07 front-and-back-matter/_acknowledgements.Rmd
Small starter fixes
Clean-up for today - ahead!
End of day
All working again after the update to Pandoc
End of day: 0

>>>>

Thanks to the creator of the oxfordown which was used

There are so many people without whom this would not have been possible:

[**Check all name spellings**]

Sharen O'Keffe
Neal Haddaway
Martin Westgate

robvis contributors

Annual reviewersLn Rupert Payne and Emma Anderson

<!-- I am a Wellcome Trust Funded PhD student with grant code 102432/Z/13/Z. The funding source had no role in the design, conduct of the study, collection, management, analysis and interpretation or preparation, review, or approval of the thesis. -->

Statistical support:

All authors who volunteered time and effort
